Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-12-14 paper/main.tex
some revision of end of discussion

\subsection{shortcomings in general}

\todo[inline]{Würde nicht so sehr auf Shortcomings eingehen}

\todo[inline]{shortcoming: no task to attend to spatial information}

@@

\todo[inline]{cf. Methods: annotation \& Methods: AO copes}
% optimal stimulus type in vision
In the visual domain, landscapes and not pictures of landmarks or buildings are
considered to be the ``optimal'' stimulus type (cf. Epstein (1998, 1999, 2003,
2008).\todo{check references}
% cateogries in primary contrasts
In the current study's primary contrast, we compared verbal cues regarding
landmarks ((\texttt{geo}; often buildings or other single aspects of a whole
scene) and elements defining the geometry of a room/locale (\texttt{groom}) to
non-spatial cues.
% we did not choose se\_new and se\_old
We did not choose the categories that contained switches from one setting to
another (\texttt{se\_new} and \texttt{se\_old}) which one might assume to
contain the auditory equivalent to the ``optimal'' visual stimulus type.
% why not se\_new or se\_old
The categories \texttt{se\_new} and \texttt{se\_old} were actually
heterogeneous: they rarely contained whole and thus a vague verbal descriptions
of landscapes (e.g. ``in a football stadium'', ``Forrest is running through the
jungle'') but mostly landmarks or buildings, and also non-spatial
cues (e.g. ``Jenny as a teenager``).
% further studies
Given that humans can identify the gist of a rich visual scene within the
duration of a single fixation \citep{henderson2003human} further studies might
investigate if categories of holistic but vague verbal descriptions of
landscapes correlate with differential hemodynamic activity in the PPA compared
to more concrete spatial cues.

% future studies
Futures studies should chose a auditory narrative that better samples the
feature space correlating with the brain process to be investigated.
% future studies: stimulus material
Future studies should probably use a different narrative that models the feature
space of spatial information ``better'' (provides more events that are more
easily classified to belong to distinctive categories).

\todo[inline]{hypothesis of increased activation correlation with changes in the
    soundscape; cf. control contrasts (e.g. \texttt{vse\_new} >
    \texttt{pe\_old}).}
% foreshadowing of narrator by soundscape
Further, verbal cues are regularly forestalled by changes of the soundscape.
% arnott
\todo[inline]{e.g. arnott2008crinkling find increased activations of PPA to
sound made by objects}
% hypothesis
We hypothesize that not just semantic information but also the mere changes of a
soundscape that cues a listener about a setting's spatial layout of could
correlate with increased activity in the PPA.

@@

\subsubsection{zpros \& cons of natural stimuli (esp. narrative) as localizer}

% quote from Hanke (2014)
\citep{hanke2014audiomovie}: the AO stimulus leaves a much larger margin for
inter-individual differences in imagining scenery.  The AO stimulus limits the
effect of an attentional focus on the selection of a subset of simultaneously
occurring auditory events, in contrast to the selection of different parts of
the visual field.

@@

@@

\todo[inline]{Conclusions aber irgendwie frage ich mich das relativ durchgehen):
Warum ist der Fokus so sehr auf Audiobook / AO, während AV doch eigentlich more
natural and engaging ist?}

% natural stimulation
Intro: Natural stimuli like movies \citep{hasson2008neurocinematics,
sonkusare2019naturalistic} or narratives \citep{honey2012not,
lerner2011topographic, silbert2014coupled} offer an easy to implement,
(continuous,) complex, immersive, task-free paradigm that more closely resembles
our natural dynamic environment than traditional experimental designs.
% why naturalisti stimuli are so cool
(see also \citep{sonkusare2019naturalistic, eickhoff2020towards,hamilton2018revolution})
% re-use of data for independent research question
Due to their continuity, complexity, and length, they offer a vast amount of
data on a variety of brain functions like low-level perception, attention,
comprehension, memory, emotions, or social interactions. This suggests the data
can later be reused for variety of totally different, independent research
questions, possibly on an individual level; increased compliance in individual
diagnostics in ``special'' populations where compliance is more difficult to
archive (pediatric or psychiatric)

% we annotated a couple of features to build contrasts
Method: The feature ``auditory spatial information'' is just one example of a
stimulus feature that can be annotated and used to build a model.
% data-driven vs. model-driven
Why we used a traditional GLM...

% results
Results: Our results demonstrate...

% conclusion: AO and AV robustness
In summary, our results across add further evidence that model-driven analyses
can be run on data from naturalistic stimuli to isolate brain activity
correlating with specific perceptual processes.
% but
Nevertheless isolation performance relies on how well the model captures
different aspects of the stimuli's feature space.

% conclusion auditory localizer
Conclusion: Thus, a complex but naturally engaging auditory stimulus like an
audiobook might in principle be used as a non-visual localizer for a variety of
brain functions in subjects who are not willing or able to follow task
instructions during brain scanning.

>>>>

\subsection{shortcomings}

\todo[inline]{SE: Würde nicht so sehr auf Shortcomings eingehen}

@@

% optimal stimulus type in vision
In the visual domain, landscapes and not pictures of landmarks or buildings are
considered to be the ``optimal'' stimulus type (cf. Epstein (1998, 1999, 2003,
2008).\todo{check references}
% cateogries in primary contrasts
In the current study's primary contrast, we compared verbal cues regarding
landmarks ((\texttt{geo}; often buildings or other single aspects of a whole
scene) and elements defining the geometry of a room or locale (\texttt{groom}) to non-spatial cues.
% we did not choose se\_new and se\_old
We did not choose the categories that contained switches from one setting to
another (\texttt{se\_new} and \texttt{se\_old}) which one might assume to
contain the auditory equivalent to the ``optimal'' visual stimulus type.
% why not se\_new or se\_old
The categories \texttt{se\_new} and \texttt{se\_old} were actually
heterogeneous: they rarely contained whole and thus a vague verbal descriptions
of landscapes (e.g. ``in a football stadium'', ``Forrest is running through the
jungle'') but mostly landmarks or buildings, and also non-spatial
cues (e.g. ``Jenny as a teenager``).
% further studies
Given that humans can identify the gist of a rich visual scene within the
duration of a single fixation \citep{henderson2003human} further studies might
investigate if categories of holistic but vague verbal descriptions of
landscapes correlate with differential hemodynamic activity in the PPA compared
to more concrete spatial cues.
% future studies
Hence, future studies might investigate if a homogenous category of wholistic
but vague verbal descriptions (e.g. ``a mountain landscape'') compared to a
homogenous categories of more specific verbal descriptions of landmarks (e.g.
``a beacon'') or houses (e.g. ``farmhouse'', ``apartment building'') lead to
different levels of hemodynamic activity.

%
\todo[inline]{shortcoming but nice hypothesis imo}
%
Cuts probably correlate with change in setting; change in soundscape anticipates
narrator (would lower detection power) or occurs in parallel with narrator; cf.
correlation of cuts to other setting (independent of familiarity) with nouns
that cue change of setting; cf. control contrasts [which ones?]
% arnott
% hypothesis
We hypothesize that not just semantic information but also the mere changes of a
soundscape that cues a listener about a setting's spatial layout of could
correlate with increased activity in the PPA.
% arnott
\todo[inline]{e.g. arnott2008crinkling finds increased activations in PPA to
sounds made by objects (that reveil object's material/identity)}

@@

@@

\todo[inline]{SE: frage ich mich das beim Durchgehen: Warum ist der Fokus so
sehr auf Audiobook / AO, während AV doch eigentlich more natural and engaging
ist? COH: at the moment, the discussion is not tailored to the topic
``naturalistic stimulus as substitute to localizer'' as it is not and should not
be the main focus}

@@

% natural stimulation
Natural stimuli like movies \citep{eickhoff2020towards,
hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
\citep{hamilton2018revolution, honey2012not, lerner2011topographic,
silbert2014coupled, wilson2008beyond} offer an easy to implement, (continuous,)
complex, immersive, task-free paradigm that more closely resembles our natural
dynamic environment than traditional experimental designs.

\begin{itemize}
\item We reuse public data for independent research question
\item GLM based on annotations to operationalize ``spatial perception''
\item Our results add evidence that model-driven analyses based in annotations
can be run on data from naturalistic stimuli to ``localize'' brain activity
correlating with specific perceptual processes.
\item ``localization performance'' relies on how well the model captures
different aspects of the stimuli's feature space.
\item PPA is functionally heterogenous region
\item a complex but naturally engaging auditory stimulus like an
audiobook might in principle be used as a non-visual localizer for a variety of
brain functions in subjects who are not willing or able to follow task
instructions during brain scanning [would state that explicitly in the summary
at the end].
\end{itemize}

% \citep{hanke2014audiomovie}: the AO stimulus leaves a much larger margin for
% inter-individual differences in imagining scenery. The AO stimulus limits the
% effect of an attentional focus on the selection of a subset of simultaneously
% occurring auditory events, in contrast to the selection of different parts of
% the visual field.
